Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-09-20 arxiv/proof_same_cov.tex

	\section{Missing Proofs of Theorem \ref{thm_many_tasks}}\label{app_proof_error_same_cov}

@@

	The third equation uses the fact that $X = Z \Sigma^{1/2}$ and Fact \ref{fact_la} in Appendix ??.

>>>>

	\section{Missing Proof of the Same Covariates Setting}\label{app_proof_error_same_cov}

@@

	The third equation uses the fact that $X = Z \Sigma^{1/2}$ and Fact \ref{fact_proof_gA} in Appendix \ref{app_tool}.
